---
title: "Task 9"
author: "Jae Wook Jung"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    code_folding: hide
    toc_float: true
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(readr)
library(knitr)
library(pander)

data <- read_rds(url("https://github.com/byuistats/data/blob/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.RDS?raw=true"))

```


#### First, create a time series plot that shows the six-month returns (y-axis) across time (x-axis) for PROS, DARTS, and DJIA

```{r}
ggplot(data, aes(x = contest_period, y = value, group = variable, color = variable)) +
  geom_line()
```

Seems DJIA has the least fluctuation return but small. 

PROS has the most high returns and fluctuates a lot.

I cannot say how much DARTS is different from PROS. DARTS fluctuates a lot and sometimes has high returns.

#### Now we need to "tidy" the data. Use the contestant_period column to create new month_end and year_end columns. (Try using separate() and/or extract() from tidyr. Save your tidy data as an .rds object)

```{r}
tidy_data <- data %>% 
  separate(contest_period, c("month_start", "month_end_year"), sep = "-") %>% 
  separate(month_end_year, c("month_end", "year_end"), sep = -4) %>% 
  select(-month_start)

tidy_data

saveRDS(tidy_data, "tidy_data.rds")
```

#### Using the new columns created above, write code that outputs a tibble of the DJIA returns that matches (as closely as possible) the table shown below (aka, “pivot_wider” the data).

```{r}
DJIA_data <- tidy_data %>% filter(variable == "DJIA")

DJIA_data <- DJIA_data %>% mutate(month_end = stringr::str_replace(month_end, "Dec.", "December")) %>% 
  mutate(month_end = stringr::str_replace(month_end, "Febuary", "February")) %>% 
  mutate(month_end = stringr::str_replace(month_end, "Decembermber", "December"))

DJIA_wide <- DJIA_data %>% 
  pivot_wider(names_from = year_end, values_from = value) %>% 
  mutate(Month = case_when(
    month_end %in% "January" ~ 1,
    month_end %in% 'February' ~ 2,
    month_end %in% "March" ~ 3,
    month_end %in% "April" ~ 4,
    month_end %in% "May" ~ 5,
    month_end %in% "June" ~ 6,
    month_end %in% "July" ~ 7,
    month_end %in% "August" ~ 8,
    month_end %in% "September" ~ 9,
    month_end %in% "October" ~ 10,
    month_end %in% "November" ~ 11,
    month_end %in% "December" ~ 12
  )) %>% 
  arrange(Month) %>% select(-c(variable, Month))

colnames(DJIA_wide)[which(names(DJIA_wide) == "month_end")] <- "Month"

DJIA_wide %>% kable()
```

