---
title: "Task 7"
author: "Jae Wook Jung"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(bakeoff)
```

#### Study the code below and run it one line at a time to see the output. Include the code in your final report. Add a comment to each line that explains what that particular line/function is doing.

```{r}
only_first_last <- ratings %>% 
  group_by(series) %>% # group by "series"
  slice(1, n()) %>% # by each "series" get rows of first and the last (number of each "series")
  mutate(which_episode = ifelse(episode == 1, "First", "Last")) %>% # make a new column with in each series there are 2 episodes and if episode is 1 it is the "first".
  ungroup() %>% # ungroup it = become back to original setting but the data set has changed.
  mutate(series_f = as.factor(series)) # make a new column that "series" are factors

ggplot(only_first_last, aes(x = which_episode, y = viewers_7day, group = series_f, color = series_f)) + # group and color by series_f
  geom_line() + # draw line graphs
  geom_point(size = 5) # draw points
```

#### Filter the data to seasons with 10 episodes. Then create one visualization that displays the 7 day ratings for each episode per series and also shows how mean ratings changed across series.

```{r}
ratings %>% group_by(series) %>% summarise(n = n()) #count series

ten_episodes <- ratings %>% group_by(series) %>% summarise(n = n()) %>% filter(n == 10) %>% pull(series)
ten_episodes

ten <- filter(ratings, series %in% ten_episodes)
```


7 day ratings for each episode per series:
```{r}
ggplot(ten, aes(x = episode, y = viewers_7day)) +
  geom_line(aes(group = series)) +
  geom_point() +
  facet_wrap(.~series) +
  theme_bw() +
  labs(title = "7 Day Ratings for Each Season", x = "Episode", y = "7 Day Ratings")
```

mean ratings changed across series:
```{r}
ten_mean <- ten %>% group_by(series) %>% summarise(mean_ratings = mean(viewers_7day))

ggplot(ten_mean, aes(x = series, y = mean_ratings)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  labs(title = "Mean 7 Day Ratings for Each Season", x = "Episode", y = "7 Day Ratings")
```

#### Discuss what you see in the graph and point out interesting features of the data. (Perhaps a little internet surfing or googling will help you explain what you see.)

The 7 day ratings were in the increasing trend until series 7. However, the ratings are a little above 9 from series 8 to 10.This can be found in both graphs.

I think `viewers_28day` seems interesting because until for a certain season, the viewers are smaller than the `viewers_7day`. However, they closely match up since season 6. So, I think analyzing more about `viewers_28day` will give a new insight.