---
title: "Case Study 12"
author: "Jae Wook Jung"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    code_folding: hide
    toc: true
    toc_float: true
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(quantmod)
library(dygraphs)
library(tidyquant)
```

```{r message=FALSE, warning=FALSE}
tickers_today <- c("CXW", "F", "GM", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT")

stocks <- tq_get(tickers_today)

stocks <- stocks %>% filter(date >= today() - years(5))
```

#### Use library(dygraphs) to build (at least two) interactive visualizations of the stock performances over the last 5 years.

##### Overall Growth

```{r message=FALSE, warning=FALSE}
stocks_avg <- stocks %>% select(symbol, date, adjusted) %>% group_by(date) %>% summarise(`average adjusted` = mean(adjusted))

stocks_avg_xts <- timetk::tk_xts(data = stocks_avg, date_var = date)

dygraph(stocks_avg_xts) %>% 
  dyRebase(value = 25000) %>% 
  dyRangeSelector()
```

##### Individual Growth

```{r message=FALSE, warning=FALSE}
stocks_inter <- stocks %>% select(symbol, date, adjusted) %>% pivot_wider(names_from = symbol, values_from = adjusted)

stock_xts <- timetk::tk_xts(data = stocks_inter, date_var = date)

dygraph(stock_xts) %>% 
  dyRebase(value = 25000) %>% 
  dyRangeSelector()
```

The investment almost doubled in the last five years. And there was a big crash in March 19, 2020. To me, most of the stocks have similar growth pattern. WDAY and KR have grown quiet well. However, GM and WDC seem to have hard time to raise their stock price.

#### Make a library(ggplot2) graphic that helps you build a solid question around how an investor would use volume in their trading strategy.

```{r message=FALSE, warning=FALSE}
stocks$gap <- stocks$high - stocks$low

options(scipen = 999)
```

```{r message=FALSE, warning=FALSE}
## Has big Volume
ggplot(stocks %>% filter(symbol %in% c("F", "KR", "T", "WFC")) %>% filter(volume < 100000000)) +
  geom_point(aes(x = volume, y = gap)) +
  geom_smooth(aes(x = volume, y = gap)) +
  theme_bw() +
  labs(title = "Stocks with Big Volumes", x = "Volumne", y = "Gap Between Day High and Low") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_continuous(labels = scales::comma) +
  facet_wrap(.~symbol)
```

```{r message=FALSE, warning=FALSE}
# Has small volume
ggplot(stocks %>% filter(!symbol %in% c("F", "KR", "T", "WFC")) %>% filter(volume < 60000000)) +
  geom_point(aes(x = volume, y = gap)) +
  geom_smooth(aes(x = volume, y = gap)) +
  theme_bw() +
  labs(title = "Stocks with Small Volumes", x = "Volumne", y = "Gap Between Day High and Low") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_continuous(labels = scales::comma) +
  facet_wrap(.~symbol)
```

Not always, but in general, the bigger volume days seem to have the bigger high and low gap. I heard that it is good to trade on the big volume days because more people will buy and sell their shares than low volume days. And sometimes big volume moment has a big drop and big rise. I wonder how people predict and do that or at least get on that flow.