---
title: "Project COVID-19"
author: "Jae Wook Jung"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.asp = 1/2, fig.fullwidth = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(flexdashboard)
library(tidyverse)
library(rgdal)
library(downloader)
library(sf)
library(fs)
library(gganimate)
library(gifski)
library(transformr)
library(lubridate)
```

```{r message=FALSE, warning=FALSE}
my_URL <- "http://thematicmapping.org/downloads/TM_WORLD_BORDERS_SIMPL-0.3.zip"

df <- tempfile() # put the file
uf <- tempfile() # directory
download(my_URL, df, mode = "wb")
unzip(df, exdir = uf)
my_map <- read_sf(uf)
file_delete(df)
dir_delete(uf)

data <- read_csv("https://covid19.who.int/WHO-COVID-19-global-data.csv")

data <- na.omit(data)

colnames(my_map)[2] <- "Country_code"

data <- left_join(data, my_map, by = "Country_code") %>% select("Date_reported", "Country_code", "Country", "New_cases", "LON", "LAT", "geometry")

# data[rowSums(is.na(data)) > 0,]

data <- data %>% filter(Country_code != "XA")
data <- data %>% filter(Country_code != "XK")
data <- data %>% filter(Country_code != "CW")
data <- data %>% filter(Country_code != "XC")
data <- data %>% filter(Country_code != "XB")
data <- data %>% filter(Country_code != "SX")
data <- data %>% filter(Country_code != "SS")
```


## Column 1

### World COVID-19 Map

```{r message=FALSE, warning=FALSE}
world <- map_data("world")

p <- ggplot(data) +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "transparent", size = 0.01
  ) +
  theme_bw() +
  #geom_polygon(data, mapping = aes(x = LON, y = LAT, group = Country_code, fill = New_cases/ 100000)) +
  #scale_fill_gradient(low = "white", high = "red") +
  geom_point(data, mapping = aes(x = LON, y = LAT, group = Country_code, size = New_cases/ 100000), color = "red") +
  theme(legend.position = "bottomleft", panel.grid = element_blank(), panel.border = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank()) +
  theme_void() +
  labs(title = "World COVID-19 Time Series", subtitle = "Date: {frame_time}", size = "New Cases\n(100,000)") +
  transition_time(Date_reported)
  
animate(p, renderer = gifski_renderer())
```

### COVID-19 World & U.S. & India Status

```{r message=FALSE, warning=FALSE}
World <- data %>% group_by(Date_reported) %>% summarise(New_cases = sum(New_cases))
World$Country_code <- "World"

US <- data %>% filter(Country_code %in% c("US", "IN")) %>% select(Date_reported, New_cases, Country_code)

worldUS <- rbind(World, US)
```

```{r message=FALSE, warning=FALSE}
options(scipen = 999)
p1 <- ggplot(worldUS) +
  geom_line(aes(x = Date_reported, y = New_cases, color = Country_code, group = Country_code)) +
  geom_point(aes(x = Date_reported, y = New_cases, color = Country_code, group = Country_code), size = 1.5) +
  scale_y_continuous(labels = scales::comma) +
  geom_segment(aes(x = Date_reported, y = New_cases, xend = max(data$Date_reported), yend = New_cases, group = Country_code), linetype = 2, colour = 'grey') + 
  geom_text(aes(x = max(data$Date_reported) - 10, y= New_cases, label = New_cases, group = Country_code), hjust = 0) +
  geom_vline(xintercept = ymd("20201214"), linetype = "dashed", color = "red", size = 0.75) +
  scale_color_manual(values = c("darkgreen", "blue", "tomato2")) +
  annotate("text", x = ymd("20201220"),y = 100000, label = "U.S. Vacciantion Start", angle = 90, size = 3, color = "red") +
  #ggrepel::geom_label_repel(data = data %>% filter(Country_code %in% c("US", "GB", "IN")), mapping = aes(x = Date_reported, y = New_cases, label = New_cases), nudge_y = -2) +
  transition_reveal(Date_reported) +
  labs(title = "COVID-19 Daily New Cases", x = "Date", y = "New Cases", color = "none") +
  theme_bw()


animate(p1, renderer = gifski_renderer())
```

## Column 2

$\bullet$ $\textbf{Background}$\
I was interested in motion graphs in the beginning of the semester. The Corona Virus Disease - 2019 (COVID-19) is still a big issue nowadays, I thought it will be fun to make time series graphs.

$\bullet$ $\textbf{COVID-19 Timeline}$

End of 2019\
\setlength{\leftskip}{2cm}
   The first COVID-19 cases were detected in Wuhan, China.\
\setlength{\leftskip}{0pt}
\
December, 2019\
\setlength{\leftskip}{2cm}
   Dr. Douglas Dwyer asked for detailed data about COVID-19, but it got rejected$^1$.\
\setlength{\leftskip}{0pt}
\
31 December, 2019\
\setlength{\leftskip}{2cm}
  China's Wuhan Municipal Health Commission reported that a cluster pneumonia case occurred in Wuhan City, Hubei Province$^2$.\
\setlength{\leftskip}{0pt}
\
12 January, 2020\
\setlength{\leftskip}{2cm}
   China publicly shared the COVID-19 gene sequence$^2$.\
\setlength{\leftskip}{0pt}
\
22 January, 2020\
\setlength{\leftskip}{2cm}
   WHO director-general Tedros Adhanom Ghebreyesus, virologists, public-health researchers, and certain government representatives did closed-door meeting and decided Public Health Emergency of International Concern (PHEIC) uncertain. However, they flipped their decision a week later$^3$.\
\setlength{\leftskip}{0pt}
\
20 February - 7 April, 2020\
\setlength{\leftskip}{2cm}
   The U.S. stock market crash$^4$. Dow Jones Industrial Average (DJIA) fell about 30% (22859.6 points which are close to 2017 February points) of its value in a month$^5$.\
\setlength{\leftskip}{0pt}
\
11 March, 2020\
\setlength{\leftskip}{2cm}
   WHO announced COVID-19 as a pandemic$^6$.\
\setlength{\leftskip}{0pt}
\
13 March, 2020\
\setlength{\leftskip}{2cm}
   Travel ban on non-US citizens$^6$.\
\setlength{\leftskip}{0pt}
\
19 March, 2020\
\setlength{\leftskip}{2cm}
   California ordered a Stay-at-Home order statewide for the first out of all the states$^6$.\
\setlength{\leftskip}{0pt}
\
14 December, 2020\
\setlength{\leftskip}{2cm}
   The first COVID-19 vaccination in the U.S given to public. A nurse in New York got Pfizer vaccine$^7$.\
\setlength{\leftskip}{0pt}
\
February - June, 2021\
\setlength{\leftskip}{2cm}
   The second wave in India. An average of 10,000 confirmed cases a day$^8$.\
\setlength{\leftskip}{0pt}
\
14 May, 2021\
\setlength{\leftskip}{2cm}
   Centers of Disease Control (CDC) announced that fully vaccinated people don't have to wear masks$^9$.\
\setlength{\leftskip}{0pt}


$\bullet$ $\textbf{Sources}$\
COVID-19 Data: [WTO COVID-19 Dashboard](https://covid19.who.int/)\
Map Coordiante Data: [thematicmapping](http://thematicmapping.org)

$^1$ https://www.bbc.com/news/world-asia-china-56054468 \
$^2$ https://www.who.int/news/item/27-04-2020-who-timeline---covid-19 \
$^3$ https://www.nature.com/articles/d41586-021-00162-4 \
$^4$ https://en.wikipedia.org/wiki/2020_stock_market_crash \
$^5$ https://www.macrotrends.net/1319/dow-jones-100-year-historical-chart \
$^6$ https://www.ajmc.com/view/a-timeline-of-covid19-developments-in-2020 \
$^7$ https://www.wsj.com/articles/covid-19-vaccinations-in-the-u-s-slated-to-begin-monday-11607941806 \
$^8$ https://www.cnbc.com/2021/05/03/india-covid-crisis-charts-show-the-severity-of-the-second-wave.html \
$^9$ https://www.cnbc.com/2021/05/13/cdc-says-fully-vaccinated-people-dont-need-to-wear-face-masks-indoors-or-outdoors-in-most-settings.html

